The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-05-13 albatros_paper.tex
HCC minor tweaks

\begin{figure}
  \begin{center} \includegraphics[width=1.0\linewidth]{Figures/albatros_2elem_schematic/albatros_2elem_schematic.pdf}
    \caption{Two-element \albatros\ pathfinder block diagram.
      Signals from two dual-polarzation LWA antennas are amplified by
      front-end active baluns (\attention{citation for FEE}).
      Antennas are connected via 100m coax cables to the back-end 
      readout electronics, which are housed in a Faraday cage denoted
      by the dashed box.  Each of the four antenna outputs is passed
      to a second-stage electronics chain consisting of filters and further amplfication.  The signals are
      digitized at 250~Msamp/s by a SNAP board, which includes an on-board FPGA that computes auto and cross spectra
      from and between the four inputs.  A Raspberry Pi controls the SNAP board and
      saves the data.}
    \label{Fig:albatros2_schem}
  \end{center}
\end{figure}

@@

The LWA active-balun front-end electronics (FEE) circuit uses a MiniCircuits GALI-74+ MMIC 
to amplify each dipole leg against ground, presenting each leg with a 50$\ohm$ impedance 
and providing a nominal gain of 25dB. The two GALI-74+ outputs are differenced using a 
passive {180\degree} hybrid coupler. The coupler output is filtered by a $\sim$150MHz lowpass, 
and receives an additional 12dB of gain from a MiniCircuits GALI-6+ MMIC. This last amplifier 
drives the output signal onto a 100m 50$\ohm$ coaxial cable. Thus, neglecting mismatch loss 
between the dipoles (electrically small in the frequency range of interest) and the 100{\ohm} 
input impedance, as well as the hybrid insertion loss ($<$1dB), the front-end electronics 
provide a gain of $\sim$37dB \cite{2012PASP..124.1090H}.

>>>>

\begin{figure}
  \begin{center} \includegraphics[width=1.0\linewidth]{Figures/albatros_2elem_schematic/albatros_2elem_schematic.pdf}
    \caption{Two-element \albatros\ pathfinder block diagram.  Signals
      from two dual-polarzation LWA antennas are amplified by
      front-end active baluns~\citep{2012PASP..124.1090H}.  Antennas
      are connected via 100m coax cables to the back-end readout
      electronics, which are housed in a Faraday cage denoted by the
      dashed box.  Each of the four antenna outputs is passed to a
      second-stage electronics chain consisting of filters and further
      amplfication.  The signals are digitized at 250~Msamp/s by a
      SNAP board, which includes an on-board FPGA that computes auto
      and cross spectra from and between the four inputs.  A Raspberry
      Pi controls the SNAP board and saves the data.}
    \label{Fig:albatros2_schem}
  \end{center}
\end{figure}

@@

The LWA active-balun front-end electronics (FEE) circuit uses a MiniCircuits GALI-74+ MMIC 
to amplify each dipole leg against ground, presenting each leg with a 50$\ohm$ impedance 
and providing a nominal gain of 25dB. The two GALI-74+ outputs are differenced using a 
passive {180\degree} hybrid coupler. The coupler output is filtered by a $\sim$150MHz lowpass, 
and receives an additional 12dB of gain from a MiniCircuits GALI-6+ MMIC. This last amplifier 
drives the output signal onto a 100m 50$\ohm$ coaxial cable. Thus, neglecting mismatch loss 
between the dipoles (electrically small in the frequency range of interest) and the 100{\ohm} 
input impedance, as well as the hybrid insertion loss ($<$1dB), the front-end electronics 
provide a gain of $\sim$37~dB~\citep{2012PASP..124.1090H}.
